\Title

### 2016-02-26 manuscript/manuscript.tex
First draft of abstract
Fixes #17

\begin{abstract}
\end{abstract}

>>>>

\begin{abstract}
    Estimating the relief of the Moho from gravity data is a computationally
    intensive non-linear inverse problem.
    What is more, the modeling must take the Earths curvature into account when
    the study area is of regional scale or greater.
    We present a regularized non-linear gravity inversion method that has a low
    computational footprint and employs a spherical Earth approximation.
    To achieve this, we combine the highly efficient Bott's method with
    smoothness regularization and a discretization of the anomalous Moho into
    tesseroids (spherical prisms).
    The computational efficiency of our method is attained by harnessing the
    fact that all matrices involved are sparse.
    The inversion results are controlled by three hyper-parameters: the
    regularization parameter, the anomalous Moho density-contrast, and the
    reference Moho depth.
    We estimate the regularization parameter using the method of hold-out
    cross-validation.
    Additionally, we estimate the density-contrast and the reference depth
    using knowledge of the Moho depth at certain points.
    We apply the proposed method to estimate the Moho depth for the South
    American continent using satellite gravity data and seismological data.
    The final Moho model is in accordance with previous gravity-derived models
    and seismological data.
    The misfit to the gravity and seismological data is worse in the Andes and
    best in oceanic areas, central Brazil and Patagonia, and along the Atlantic
    coast.
    Similarly to previous results, the model suggests a thinner crust of 30-35
    km under the Andean foreland basins.
    Discrepancies with the seismological data are greatest in the Guiana
    shield, the central Solimões and Amazon basins, the Paraná basin, and the
    Borborema province.
    These differences suggest the existence of crustal or mantle density
    anomalies that were unaccounted for during gravity data processing.
\end{abstract}
